### 2017-10-01 TF-vldb2018/sec-expt.tex

 We used the following datasets and settings.

%\subsection{Experimental Settings}
%We used the following real-life and synthetic datasets.
\vspace{-0.3ex}
\etitle{Data graphs.} We used two real-life and a synthetic datasets.

@@

%\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.

>>>>

 We used the following real-life and synthetic datasets.

%\subsection{Experimental Settings}

\vspace{-0.3ex}
\etitle{Real-life graphs.} We used two real-life graphs.

\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.

\etitle{Synthetic graph generator.} We generated synthetic graphs (\synthetic) with community structures as existed in real-life, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.

\eat{
 We used the following datasets and settings.

\etitle{Data graphs.} We used two real-life and a synthetic datasets.

@@

%\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.
}%%%EAT
